Survival - frequentist, single outcome

### 2020-11-26 manuscript/single_outcome_coxph.Rmd
Cleaning up, finishing touches on manuscript, work on supplement

hypothesis_res_list[["competing_hcq_comorbidities_sum"]] <-
  rbind(
  frequentist_hypothesis_res_from_coxph1(hypotheses$hcq_reduces_death, 
                                         point_estimate = coef(m1)[1],
                                         adjusted = "age, sex, comorbidities (sum)", 
                                         test_stat = anova(m1,m0,test='Chisq')[2,2],
                                         df = anova(m1,m0,test='Chisq')[2,3],
                                         p = anova(m1,m0,test='Chisq')[2,4],
                                         ci_low = confint(m1)[1,1],
                                         ci_high = confint(m1)[1,2]),
  frequentist_hypothesis_res_from_coxph1(hypotheses$hcq_increases_discharged, 
                                         point_estimate = coef(mt1)[1],
                                         adjusted = "age, sex, comorbidities (sum)", 
                                         test_stat = anova(mt1,mt0,test='Chisq')[2,2],
                                         df = anova(mt1,mt0,test='Chisq')[2,3],
                                         p = anova(mt1,mt0,test='Chisq')[2,4],
                                         ci_low = confint(mt1)[1,1],
                                         ci_high = confint(mt1)[1,2])
  )
hypothesis_res_list[["competing_hcq_comorbidities_sum"]]

>>>>

hypothesis_res_list[["competing_hcq_comorbidities_sum"]] <-
  rbind(
  frequentist_hypothesis_res_from_coxph1(hypotheses$hcq_death, 
                                         point_estimate = coef(m1)[1],
                                         adjusted = "age, sex, hospital, comorbidities (sum)", 
                                         test_stat = anova(m1,m0,test='Chisq')[2,2],
                                         df = anova(m1,m0,test='Chisq')[2,3],
                                         p = anova(m1,m0,test='Chisq')[2,4],
                                         ci_low = confint(m1)[1,1],
                                         ci_high = confint(m1)[1,2]),
  frequentist_hypothesis_res_from_coxph1(hypotheses$hcq_hospital, 
                                         point_estimate = -coef(mt1)[1],
                                         adjusted = "age, sex, hospital, comorbidities (sum)", 
                                         test_stat = anova(mt1,mt0,test='Chisq')[2,2],
                                         df = anova(mt1,mt0,test='Chisq')[2,3],
                                         p = anova(mt1,mt0,test='Chisq')[2,4],
                                         ci_low = -confint(mt1)[1,2],
                                         ci_high = -confint(mt1)[1,1])
  )
hypothesis_res_list[["competing_hcq_comorbidities_sum"]]
